---
  output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# mrgda
A data assembly validation tool designed to identify errors in derived data sets. 
`nm_validate` runs a series of pass/fail checks on NONMEM data sets and `nm_summary` 
provides a quick visualization of this data. 

## Background
Often data sets are derived according to a data specification file. This package 
leverages the information within this file to validate the data set. It is suggested
that the data specification file be made in `yaml` format. An example of one can be 
found in `inst/derived/pk.yml`.

Within the setup section, `flags` are defined. In order to use `mrgda` the
names of the flags must match those shown below:

```{r, eval=FALSE}
flags:
  id: [ID] # Unique subject ID
  num: [NUM] # Unique row ID
  study: [STUDYID] # Study ID
  primary_keys: [EVID, DVID] # Variables such as EVID and DVID where you anticipate no duplicate combinations
  time: [TIME] # Time 
  bl_cat_cov: [SEX, RACE] # Baseline categorical covariate
  tv_cat_cov: [TIMECAT] # Time-varying categorical covariate
  bl_cont_cov: [WTBL, BMIBL, AGEBL] # Baseline continuous covariate
  tv_cont_cov: [WT] # Time-varying continuous covariate
```

*IMPORTANT NOTE* - it is not necessary to have a variable provided for each flag. Adding variables to each of the flags is optional, 
however the significance of the output will be decreased with the less information provided in flags.

## Documentation
Public documentation of all functions is hosted at [https://metrumresearchgroup.github.io/mrgda/](https://metrumresearchgroup.github.io/mrgda/)

## Development

`mrgda` uses [pkgr](https://github.com/metrumresearchgroup/pkgr) to manage
development dependencies and [renv](https://rstudio.github.io/renv/) to
provide isolation. To replicate this environment,

1.  clone the repo

2.  install pkgr

3.  open package in an R session and run `renv::init(bare = TRUE)`

    -   install `renv` \> 0.8.3-4 into default `.libPaths()` if not
        already installed

4.  run `pkgr install` in terminal within package directory

5.  restart session

Then, launch R with the repo as the working directory (open the project
in RStudio). renv will activate and find the project library.

## Package coverage

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
if (basename(getwd()) == "docs") {
  knitr::opts_knit$set(root.dir = file.path(getwd(), ".."))
}

```

```{r}
covr::package_coverage()
```
