---
  output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

## Overview

mrgda is a NONMEM data assembly helper, providing a set of functions that help
validate your derived data set. Working hand in hand with your data specification,
`nm_validate()` checks for common data set errors such as:

* Duplicated events
* Non-unique baseline covariates
* Missing covariates

To use mrgda optimally, you are encouraged to set up your data specification file
in `yaml` format, similar to the example found [here](https://github.com/metrumresearchgroup/mrgda/blob/main/inst/derived/pk.yml) and
discussed further in the Setup section below.

## Setup

Before running mrgda, a `flags` parameter needs to be defined within the `SETUP` 
section of the data specification yaml file. All relevant column names need to 
be defined for each of the following flags:

* `id` - subject identification (typically ID)
* `study` - study identification
* `primary_keys` - event defining variables (ie. EVID and DVID)
* `time` - time
* `bl_cat_cov` - baseline categorical covariates
* `tv_cat_cov` - time-varying categorical covariates
* `bl_cont_cov` - baseline continuous covariates
* `tv_cont_cov` - time-varying continuous covariates

Note in the example below that multiple variables can be listed for each flag
and that not all flags need to be defined. For instance, no time-varying 
categorical covariates are listed below.

```{r, eval=FALSE}
SETUP:
  flags:
    id: [ID]
    study: [STUDYID]
    primary_keys: [EVID, DVID]
    time: [TIME]
    bl_cat_cov: [SEX, RACE]
    bl_cont_cov: [WTBL, BMIBL, AGEBL] 
    tv_cont_cov: [WT]
```

## Usage

```{r, include=FALSE}

nm_spec <- yspec::ys_load(system.file("derived", "pk.yml", package = "mrgda"))
nm <- readr::read_csv(system.file("derived", "pk.csv", package = "mrgda"), na = ".", show_col_types = FALSE)
nm_errors <- readr::read_csv(system.file("derived", "pk-errors.csv", package = "mrgda"), na = ".", show_col_types = FALSE)

nm_ex_df <- dplyr::tibble(
     AGE = c(45, 82, 73),
     WT = c(64, 23, 92),
     SC = c(1.02, 1.04, 1.98),
     SEX = c(1, 2, 1),
     RACE = c(1, 2, 3))

```

#### Data validation

`nm_validate()` outputs the results of the pass/fail checks. If a check fails,
the user will be provided code to help identify where the error is in the data.

```{r, comment=NA}
library(mrgda)

nm_validate(.data = nm_errors, .spec = nm_spec, .error_on_fail = FALSE)

```

## Documentation
Public documentation of all functions is hosted at [https://metrumresearchgroup.github.io/mrgda/](https://metrumresearchgroup.github.io/mrgda/)


## Development

`mrgda` uses [pkgr](https://github.com/metrumresearchgroup/pkgr) to manage
development dependencies and [renv](https://rstudio.github.io/renv/) to
provide isolation. To replicate this environment,

1.  clone the repo

2.  install pkgr

3.  open package in an R session and run `renv::init(bare = TRUE)`

    -   install `renv` \> 0.8.3-4 into default `.libPaths()` if not
        already installed

4.  run `pkgr install` in terminal within package directory

5.  restart session

Then, launch R with the repo as the working directory (open the project
in RStudio). renv will activate and find the project library.

## Getting help

If you encounter a clear bug, please file an issue with a minimal reproducible example on [mrgda](https://github.com/mrgda/issues). 

```{r setup, include = FALSE}
## Package coverage
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
if (basename(getwd()) == "docs") {
  knitr::opts_knit$set(root.dir = file.path(getwd(), ".."))
}

```

```{r, include=FALSE}
covr::package_coverage()
```
