---
title: "annotate-da-code"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{annotate-da-code}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a vignette to help you become familiar with using `annotate_da()`.
Check out the <a href="https://metrumresearchgroup.github.io/mrgda/reference/annotate_da.html"
target="_blank">function documentation</a> for additional background and examples.

`annotate_da()` prints a formatted message containing the result of a provided expression.
This function is intended to be run interactively in the R console to aid in code
understanding, transfer and debugging.

Below, we will go through a few examples cases using `annotate_da()`.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ""
)
```

```{r load packages, results = 'hide', message=FALSE, warning=FALSE}
library(mrgda)
library(dplyr)
```

# Setup

We will use `annotate_da()` to document data manipulations and checks on the derived PK
data set from `mrgda`.

```{r, message=FALSE}
pk_data <- readr::read_csv(system.file("derived/pk.csv", package = "mrgda"))
```

# Using annotate_da()

Before performing a data manipulation, we can use `annotate_da()` to document why
it is needed. This will help transfer knowledge of assumptions/decisions made
to future authors or reviewers.

```{r message=FALSE, warning=FALSE, include=FALSE}
pk_data <-
  pk_data %>% 
  dplyr::mutate(
    DV = dplyr::if_else(ID == 1 & TIME == 0.68, "15000", DV)
  )
```

For instance, if we're planning to exclude a record we believe is an outlier, 
we can first use `annotate_da()` to show where in the data the issue exists.

```{r}
mrgda::annotate_da("ID = 1 has outlier in PK data, will remove", {
  pk_data %>% 
    filter(ID == 1, DVID == 2, TIME < 24) %>% 
    select(ID, TIME, TAD, DV, DVID, EVID)
})
```

This not only explains the issue, but shows where in the data it occurs. 
Additionally, the formatting of the message separates itself from the rest of
the console outputs, helping it be more easily seen.

## Arguments

Users need to provide two arguments to `annotate_da()`. The first is a message
to display in the header and the second is an expression to display the result of.

As shown previously, this expression could be in the form of a data.frame.

```{r}
mrgda::annotate_da("Show the first few records of ID = 2 from the pk_data data.frame", {
  pk_data %>% 
    filter(ID == 2) %>% 
    select(ID, TIME, DV, EVID) %>% 
    head()
})
```

A vector can also be provided, such as one containing all the unique studies from the data set.

```{r}
mrgda::annotate_da("Show a vector of all studies in the data set", {
  pk_data %>% 
    distinct(STUDYID) %>% 
    pull(STUDYID)
})
```

Calculations can even be performed.

```{r}
mrgda::annotate_da("Total number of PK records that are not BLQ and doses", {
  nrow(pk_data %>% filter(DVID == 2, BLQ == 1)) +
    nrow(pk_data %>% filter(DVID ==1))
})
```

Essentially, anything that can be evaluated in the console can be provided
as the `.expr` argument. 

