---
title: "assigning-id"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{assigning-id}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a vignette to help you become familiar with using `assign_id()`. 
Check out the <a href="https://metrumresearchgroup.github.io/mrgda/reference/assign_id.html"
target="_blank">function documentation</a> for additional background and examples.

`assign_id()` helps you assign a unique numeric identifier to each
subject in your data set. Its purpose is to ensure the same numeric identifier
is consistently assigned to each subject throughout a project. 

Below, we will go through the two main use cases of `assign_id()`. These are 
when you are assigning ID either for the first time or according to an existing file.

# Load packages

```{r setup_interactive, include=FALSE}
if (interactive() || isTRUE(getOption('knitr.in.progress'))) {
  devtools::load_all()
}
```

```{r setup, message=FALSE}
library(mrgda)
library(dplyr)
```

# Setup

We will use the example derived PK data set from `mrgda`. 

For the purposes of this vignette, a subject identifier column
`USUBJID` is created and the `ID` column is removed. 

```{r, message=FALSE}
pk_data <-
  readr::read_csv(system.file("derived/pk.csv", package = "mrgda")) %>%
  mutate(USUBJID = paste0(STUDYID, "-", ID)) %>%
  select(-ID)
```

# Initial ID assignment

When creating a new data set where IDs have not been assigned previously,
`assign_id()` only requires two arguments:

- the data to append the `ID` column to (.data)
- the subject identifier column name (.subject_col)

```{r}
data_w_id <-
  pk_data %>%
  assign_id(.subject_col = "USUBJID")
```

A summary is shown in the R console, detailing how many unique subjects
were assigned an ID. Notice as well that the only change to `pk_data` 
is one additional column.

```{r, echo=FALSE}
print(paste0("Size of pk_data ", dim(pk_data)[1], " x ", dim(pk_data)[2]))
print(paste0("Size of data_w_id ", dim(data_w_id)[1], " x ", dim(data_w_id)[2]))
```

# Existing ID assignment

When data sets are updated or new subsets are created, `assign_id()`
ensures the ID mapping is consistent throughout. To do this, we can
leverage the `.previously_derived_path` argument.

First we will create a new data set `pk_data_reordered` which has the
same contents as `pk_data` but is arranged in a different order.

```{r}
pk_data_reordered <-
  pk_data %>%
  arrange(USUBJID)

head(pk_data_reordered %>% distinct(USUBJID))
head(pk_data %>% distinct(USUBJID))
```

```{r, include=FALSE}
# Writing out data to a temporary location in order to use .previously_derived_path below
lookup_path <- paste0(tempfile(), ".csv")
mrgda:::write_csv_dots(
  x = data_w_id,
  file = lookup_path
)
```

However, when we inform `assign_id()` we want the ID assignment to 
match that of `data_w_id`, then the mapping is consistent.

```{r, message=FALSE}
data_w_id_reordered <-
  pk_data_reordered %>%
  assign_id(.previously_derived_path = lookup_path, .subject_col = "USUBJID")
```

Notice that despite the sorting differences, both `data_w_id` and `data_w_id_reordered`
have the same ID assignment.

```{r}
head(data_w_id %>% distinct(USUBJID, ID) %>% arrange(ID))
head(data_w_id_reordered %>% distinct(USUBJID, ID) %>% arrange(ID))
```

# New subjects

In the event that there are new subjects in your data that were
not present in the previously derived data set, then a new unique
ID will be assigned to them.

`assign_id()` does this by finding the maximum ID present in the
previous data and setting all new ID's higher than it. An example
of this is shown below.

```{r}
old_data <- dplyr::tibble(USUBJID = c("A", "B", "C", "D"), ID = c(1, 2, 4, 19))
lookup_path <- paste0(tempfile(), ".csv")
mrgda:::write_csv_dots(
  x = old_data,
  file = lookup_path
)

data <- dplyr::tibble(USUBJID = c("E", "F", "G"))
assign_id(.data = data, .subject_col = "USUBJID", .previously_derived_path = lookup_path)
```

Notice how the largest ID in the previous data set was 19. Since subjects `E`, `F` and `G` 
were not present in `old_data` their ID's were all set to be larger than 19.
