---
title: "Getting Started with mrgda"
author: "Michael McDermott"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  include = FALSE
)
```

# Introduction

This "Getting Started with mrgda" vignette takes the user through some basic scenarios for using `mrgda` to verify that a data set has been derived according to its data specification and common data assembly errors have been avoided. 

```{r load packages, results = 'hide', message=FALSE, warning=FALSE}
library(mrgda)
library(dplyr)
```

`mrgda` is composed of two main functions. `nm_validate` performs a series of pass/fail checks on the dataset, using the flags in the data specification as a guide. `nm_summary` offers to the ability to view high level summaries of the data via tables & figures. Together, these tools are intended to improve the accuracy of derived data sets.

# Data Specification Flags

Often data sets are derived according to a data specification file. This package 
leverages the information within this file to validate the data set. It is suggested
that the data specification file be made in `yaml` format. 

Within the setup section of the `yaml` file, `flags` are defined. In order to use `mrgda` the
names of the flags must match those shown below. Adding variables to these flags will inform `mrgda` of
what columns are of interest in the data set.

```{r, eval=FALSE}
flags:
  id: [ID] # Unique subject ID
  study: [STUDYID] # Study ID
  primary_keys: [EVID, DVID] # variables such as EVID and DVID where you anticipate no duplicate combinations
  time: [TIME] # Time
  bl_cat_cov: [SEX, RACE] # Baseline categorical covariate
  tv_cat_cov: [TIMECAT] # Time-varying categorical covariate
  bl_cont_cov: [WTBL, BMIBL, AGEBL] # Baseline continuous covariate
  tv_cont_cov: [WT] # Time-varying continuous covariate
```

In the specification above, we are identifying the `SEX` and `RACE` columns as baseline categorical covariates.
`nm_validate` will use this information and perform checks such as, does each subject only have 1 unique baseline
covariates combination?

Similarily, `nm_validate` will use the `primary_keys` and `time` flag to check if every row within this subset of columns 
is unique. If some rows are not unique, this would indicate a duplicate observation in the data set.

# Non-unique baseline covariates checks (NONMEM)

With the data specification flags set up, we can load the data set and specification file into R as such.
We will also create a `nm1` dataset, that purposefully has non-unique baseline covariates.

```{r}
nm_spec <- yspec::ys_load(system.file("derived", "pk.yml", package = "mrgda"))
nm <- readr::read_csv(system.file("derived", "pk.csv", package = "mrgda"), na = ".", show_col_types = FALSE)

nm1 <- nm %>% dplyr::mutate(AGEBL = replace(AGEBL, ID == 4 & NUM == 68, 52))
```

Now we can run `nm_validate` on this modified data set.

```{r}
nm_validate(.data = nm1, .spec = nm_spec, .error_on_fail = FALSE)
```

As expected, the modified data set failed the baseline covariate check. Notice how `nm_validate` outputs the 
number of passed & failed tests, along with the rows from the data that caused the issue.

# Missing time-varying covariate checks (NONMEM)

A similar error message will appear for other checks as well. For instance, another common error during 
data assembly is leaving time-varying covariates unfilled. If `nm_validate` finds a case of this, it will
return the following:

```{r}
nm %>%
    dplyr::mutate(WT = replace(WT, ID == 4, NA)) %>%
    nm_validate(.spec = nm_spec, .error_on_fail = FALSE)
```

Notice how `nm_validate` outputs the cause of the error along with the rows in question.

# Flags

As the examples show above, the flags specified in the data specification inform `nm_validate` of the 
relevant columns to check for each test. If no variables are provided to a flag, the tests will still
run however their results will not hold significance. 

The value and benefit of using `mrgda` is dependent on the amount of information included in the
flags. As more relevant variables are added, the significance of the tests passing increase as well.
