---
title: "Clinical Trial Protocol"
subtitle: "Reconstructed from CDISCPILOT01 Source Data"
author: "mrgda example-project"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    number_sections: true
geometry: margin=0.8in
fontsize: 10pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

data_dir <- "."
read_domain <- function(domain) {
  haven::read_xpt(file.path(data_dir, paste0(domain, ".xpt"))) |>
    as.data.frame()
}

fmt <- function(x) {
  x <- as.character(x)
  x[is.na(x) | x == ""] <- "Not reported"
  x
}

dm <- read_domain("dm")
ex <- read_domain("ex")
lb <- read_domain("lb")
pc <- read_domain("pc")
vs <- read_domain("vs")

study_id <- unique(dm$STUDYID)
countries <- paste(sort(unique(dm$COUNTRY)), collapse = ", ")
site_count <- length(unique(dm$SITEID))
randomized_dm <- subset(dm, ARM != "Screen Failure")
treated_dm <- subset(dm, ACTARM != "Screen Failure")

study_start <- min(as.Date(dm$RFSTDTC), na.rm = TRUE)
study_end <- max(as.Date(dm$RFENDTC), na.rm = TRUE)
exposure_start <- min(as.Date(ex$EXSTDTC), na.rm = TRUE)
exposure_end <- max(as.Date(ex$EXENDTC), na.rm = TRUE)

arm_table <- as.data.frame(table(dm$ARM), stringsAsFactors = FALSE)
names(arm_table) <- c("Planned Arm", "Subjects")

actual_arm_table <- as.data.frame(table(dm$ACTARM), stringsAsFactors = FALSE)
names(actual_arm_table) <- c("Actual Arm", "Subjects")

sex_table <- as.data.frame(table(dm$SEX), stringsAsFactors = FALSE)
names(sex_table) <- c("Sex", "Subjects")

race_table <- as.data.frame(sort(table(dm$RACE), decreasing = TRUE), stringsAsFactors = FALSE)
names(race_table) <- c("Race", "Subjects")

ethnic_table <- as.data.frame(table(dm$ETHNIC), stringsAsFactors = FALSE)
names(ethnic_table) <- c("Ethnicity", "Subjects")

site_table <- as.data.frame(sort(table(dm$SITEID), decreasing = TRUE), stringsAsFactors = FALSE)
names(site_table) <- c("Site", "Subjects")

ex_regimens <- unique(ex[, c("EXTRT", "EXDOSE", "EXDOSU", "EXDOSFRM", "EXDOSFRQ", "EXROUTE")])
ex_regimens <- ex_regimens[order(ex_regimens$EXDOSE), ]
names(ex_regimens) <- c("Treatment", "Dose", "Unit", "Form", "Frequency", "Route")

ex_visits <- unique(ex[, c("VISITNUM", "VISIT", "VISITDY")])
ex_visits <- ex_visits[order(ex_visits$VISITNUM), ]
names(ex_visits) <- c("Visit Number", "Visit", "Study Day")

all_visits <- unique(rbind(
  lb[, c("VISITNUM", "VISIT", "VISITDY")],
  pc[, c("VISITNUM", "VISIT", "VISITDY")],
  vs[, c("VISITNUM", "VISIT", "VISITDY")]
))
all_visits <- all_visits[order(all_visits$VISITNUM), ]
names(all_visits) <- c("Visit Number", "Visit", "Study Day")

scheduled_visits <- subset(all_visits, !grepl("UNSCHEDULED", Visit) & !is.na(`Study Day`))

lb_cats <- as.data.frame(sort(table(fmt(lb$LBCAT)), decreasing = TRUE), stringsAsFactors = FALSE)
names(lb_cats) <- c("Category", "Results")

lb_nri <- as.data.frame(sort(table(fmt(lb$LBNRIND)), decreasing = TRUE), stringsAsFactors = FALSE)
names(lb_nri) <- c("Reference Range Indicator", "Results")

lb_tests <- unique(lb[, c("LBCAT", "LBTESTCD", "LBTEST", "LBSTRESU")])
lb_tests$LBCAT <- fmt(lb_tests$LBCAT)
lb_tests$LBSTRESU <- fmt(lb_tests$LBSTRESU)
lb_tests <- lb_tests[order(lb_tests$LBCAT, lb_tests$LBTESTCD), ]
names(lb_tests) <- c("Category", "Code", "Test", "Unit")

pc_tests <- unique(pc[, c("PCTESTCD", "PCTEST", "PCSTRESU", "PCSPEC", "PCLLOQ")])
pc_tests <- pc_tests[order(pc_tests$PCSPEC, pc_tests$PCTESTCD), ]
names(pc_tests) <- c("Code", "Analyte", "Unit", "Specimen", "Lower Limit")

pc_tpts <- unique(pc[, c("VISIT", "VISITDY", "PCTPT", "PCTPTNUM")])
pc_tpts <- pc_tpts[order(pc_tpts$VISITDY, pc_tpts$PCTPTNUM), ]
names(pc_tpts) <- c("Visit", "Study Day", "Nominal Time Point", "Nominal Hour")

vs_tests <- unique(vs[, c("VSTESTCD", "VSTEST", "VSPOS", "VSLOC", "VSSTRESU")])
vs_tests$VSPOS <- fmt(vs_tests$VSPOS)
vs_tests$VSLOC <- fmt(vs_tests$VSLOC)
vs_tests$VSSTRESU <- fmt(vs_tests$VSSTRESU)
vs_tests <- vs_tests[order(vs_tests$VSTESTCD, vs_tests$VSPOS, vs_tests$VSLOC), ]
names(vs_tests) <- c("Code", "Vital Sign", "Position", "Location", "Unit")

death_count <- sum(dm$DTHFL == "Y", na.rm = TRUE)
```

\newpage

# Administrative Information

This protocol is reconstructed from the XPT source data in `inst/example-project/data/source/CDISCPILOT01`. It is intended for example-project documentation and data interpretation. It is not an original sponsor-approved protocol and must not be used to conduct human subject research.

**Study identifier:** `r study_id`

**Protocol title:** A randomized, placebo-controlled, parallel-group study of transdermal Xanomeline in subjects with mild to moderate Alzheimer's disease.

**Investigational product:** Xanomeline transdermal patch.

**Control:** Matching placebo transdermal patch.

**Country and sites:** `r countries`; `r site_count` sites.

**Observed subject reference period:** `r format(study_start, '%Y-%m-%d')` to `r format(study_end, '%Y-%m-%d')`.

**Observed exposure period:** `r format(exposure_start, '%Y-%m-%d')` to `r format(exposure_end, '%Y-%m-%d')`.

# Protocol Synopsis

```{r synopsis}
synopsis <- data.frame(
  Item = c(
    "Design",
    "Population",
    "Sample size in source data",
    "Treatment groups",
    "Route and dosage form",
    "Primary objective",
    "Key assessments",
    "PK sampling",
    "Key scheduled visits"
  ),
  Description = c(
    "Multicenter, randomized, placebo-controlled, parallel-group clinical pharmacology and safety study.",
    "Adult and older adult subjects with Alzheimer's disease, inferred from the CDISC pilot Xanomeline study context and treatment program.",
    paste0(nrow(dm), " subjects in demographics, including ", nrow(randomized_dm), " non-screen-failure records and ", nrow(treated_dm), " records with non-screen-failure actual treatment."),
    paste(sort(unique(dm$ARM)), collapse = "; "),
    "Once-daily transdermal patch.",
    "To evaluate safety, tolerability, and pharmacokinetic exposure for Xanomeline low-dose and high-dose patches compared with placebo.",
    "Exposure, laboratory tests, pharmacokinetic concentrations, and vital signs.",
    "Plasma and urine Xanomeline concentrations at baseline from pre-dose through 48 hours post-dose.",
    paste(paste0(scheduled_visits$Visit, " (Day ", scheduled_visits$`Study Day`, ")"), collapse = "; ")
  ),
  check.names = FALSE
)
knitr::kable(synopsis, longtable = TRUE)
```

# Background and Rationale

The CDISCPILOT01 source package contains transdermal Xanomeline exposure records, laboratory results, pharmacokinetic concentrations, and vital signs. The treatment arms include placebo, Xanomeline low dose, and Xanomeline high dose. This reconstructed protocol therefore describes a placebo-controlled Xanomeline study with primary emphasis on safety, tolerability, and pharmacokinetics.

The available source package does not include efficacy, adverse event, disposition, concomitant medication, or medical history domains. Those omissions limit reconstruction of the original clinical rationale and endpoint hierarchy. The protocol below uses the available source data as the controlling evidence and flags inferred content where appropriate.

# Objectives and Endpoints

## Primary Objective

To characterize the safety and tolerability of once-daily transdermal Xanomeline low-dose and high-dose patches compared with placebo.

## Secondary Objectives

1. To characterize plasma and urine Xanomeline concentration-time profiles after dosing.
2. To summarize laboratory safety findings by category and reference range indicator.
3. To summarize vital sign findings over scheduled and unscheduled visits.
4. To summarize exposure to placebo, Xanomeline 54 mg, and Xanomeline 81 mg transdermal patches.

## Endpoints

Primary safety endpoints include laboratory reference range indicators, vital sign values, deaths recorded in demographics, and exposure interruptions or dosing patterns where available. Pharmacokinetic endpoints include observed Xanomeline concentration by matrix, nominal time point, and visit.

Because an adverse event domain is not present in this source package, treatment-emergent adverse event incidence cannot be reconstructed from these files.

# Study Design

This is reconstructed as a multicenter, randomized, placebo-controlled, parallel-group study. Subjects were screened, randomized to placebo or one of two Xanomeline dose levels, and followed through Week 24 with additional Week 26 or retrieval records represented in vital signs. Exposure records show dosing at baseline, Week 2, and Week 24.

```{r planned-arms}
knitr::kable(arm_table, caption = "Planned Treatment Arms")
knitr::kable(actual_arm_table, caption = "Actual Treatment Arms")
```

```{r sites}
knitr::kable(head(site_table, 20), caption = "Subjects by Site")
```

# Study Population

## Inclusion Criteria

Based on the source data and the CDISC pilot Xanomeline context, eligible subjects would have met all of the following criteria:

1. Adult or older adult male or female subjects.
2. Clinical diagnosis consistent with Alzheimer's disease.
3. Ability to receive a transdermal patch and complete protocol-required safety and PK assessments.
4. Availability for follow-up through Week 24.
5. Written informed consent provided by the subject or legally authorized representative.

## Exclusion Criteria

Subjects would have been excluded for any of the following:

1. Clinically significant unstable medical condition that could confound safety assessment.
2. Screening laboratory or vital sign finding considered clinically unacceptable by the investigator.
3. Known hypersensitivity or contraindication to Xanomeline or patch components.
4. Use of prohibited concomitant medications or participation in another interventional study.
5. Any condition preventing reliable PK sampling or follow-up.

## Demographic Characteristics in Source Data

```{r demographics}
demo_summary <- data.frame(
  Characteristic = c(
    "Subjects",
    "Non-screen-failure planned treatment records",
    "Non-screen-failure actual treatment records",
    "Age, mean",
    "Age, median",
    "Age, range",
    "Female",
    "Male",
    "Deaths flagged in demographics"
  ),
  Value = c(
    nrow(dm),
    nrow(randomized_dm),
    nrow(treated_dm),
    round(mean(dm$AGE, na.rm = TRUE), 1),
    median(dm$AGE, na.rm = TRUE),
    paste0(min(dm$AGE, na.rm = TRUE), "-", max(dm$AGE, na.rm = TRUE), " years"),
    sum(dm$SEX == "F"),
    sum(dm$SEX == "M"),
    death_count
  )
)
knitr::kable(demo_summary)
```

```{r demographic-tables}
knitr::kable(sex_table, caption = "Sex")
knitr::kable(race_table, caption = "Race")
knitr::kable(ethnic_table, caption = "Ethnicity")
```

# Investigational Product and Administration

The investigational product is Xanomeline administered as a once-daily transdermal patch. Exposure records include placebo patches and active Xanomeline patches at 54 mg and 81 mg.

```{r exposure-regimens}
knitr::kable(ex_regimens, caption = "Exposure Regimens")
knitr::kable(ex_visits, caption = "Exposure Visits")
```

Treatment compliance, patch application site rotation, accountability, and dose modification rules are not represented in the source domains and would need to be supplied by the original protocol or operational manuals.

# Schedule of Assessments

The following visits are represented across the source domains. Unscheduled visits are retained because the laboratory and vital sign data include them.

```{r visits}
knitr::kable(all_visits, longtable = TRUE, caption = "Visits Represented in Source Data")
```

```{r soa}
soa <- data.frame(
  Assessment = c(
    "Demographics",
    "Exposure",
    "Laboratory tests",
    "Pharmacokinetic concentrations",
    "Vital signs"
  ),
  Screening = c("X", "", "X", "", "X"),
  Baseline = c("", "X", "X", "X", "X"),
  `Weeks 2-24` = c("", "X", "X", "", "X"),
  `Week 26/Retrieval` = c("", "", "", "", "X"),
  Unscheduled = c("", "", "X", "", "X"),
  check.names = FALSE
)
knitr::kable(soa, caption = "Reconstructed Schedule of Assessments")
```

# Safety Assessments

## Laboratory Assessments

Laboratory testing includes chemistry, hematology, urinalysis, and additional miscellaneous results. The source package contains `r nrow(lb)` laboratory records.

```{r labs}
knitr::kable(lb_cats, caption = "Laboratory Results by Category")
knitr::kable(lb_nri, caption = "Laboratory Results by Reference Range Indicator")
knitr::kable(lb_tests, longtable = TRUE, caption = "Laboratory Tests")
```

## Vital Signs

Vital signs include blood pressure, pulse rate, height, temperature, and weight. Blood pressure and pulse were collected in supine and standing positions where applicable.

```{r vitals}
knitr::kable(vs_tests, longtable = TRUE, caption = "Vital Sign Parameters")
```

## Deaths

The demographics domain contains `r death_count` subjects flagged with death. The source package available here does not contain adverse event, disposition, or death-detail domains, so causality, timing relative to treatment, and event narratives cannot be reconstructed from these files.

# Pharmacokinetic Assessments

The pharmacokinetic concentration domain contains `r nrow(pc)` records for Xanomeline in plasma and urine. Sampling is represented at baseline from pre-dose through 48 hours post-dose, including interval collections for urine.

```{r pk}
knitr::kable(pc_tests, caption = "PK Analytes and Specimens")
knitr::kable(pc_tpts, longtable = TRUE, caption = "PK Nominal Time Points")
```

PK analyses should summarize concentration-time data by treatment, specimen, and nominal time point. Values below the lower limit of quantification should be handled using predefined rules before noncompartmental analysis or descriptive summaries.

# Statistical Considerations

All analyses for this reconstructed protocol should be descriptive. The safety analysis set should include all subjects with non-screen-failure actual treatment assignment, using the demographics actual arm field as the available proxy for treatment received. PK summaries should include subjects with at least one quantifiable or reportable PK concentration record.

Continuous variables should be summarized with n, mean, standard deviation, median, minimum, and maximum. Categorical variables should be summarized with counts and percentages. Laboratory and vital sign summaries should be presented by visit and treatment arm. PK concentrations should be summarized by specimen, nominal time point, and actual treatment arm.

No formal hypothesis testing is specified because this reconstruction is based on source domains rather than an original statistical analysis plan.

# Data Handling and Quality Control

The source package should be checked for:

1. Consistency of `STUDYID`, `USUBJID`, site, arm, and actual arm values across domains.
2. Consistency of visit numbers, visit names, and study days.
3. Completeness of exposure records for treated subjects.
4. Validity of laboratory reference range indicators and standardized units.
5. Consistency of PK time point labels and nominal time values.
6. Traceability from generated outputs to the source XPT records.

# Ethical and Regulatory Considerations

For an actual trial, the protocol and informed consent materials would require institutional review board or ethics committee approval before initiation. The study would be conducted in accordance with Good Clinical Practice, applicable regulations, and the Declaration of Helsinki.

# Limitations of Reconstruction

This document is inferred from available XPT source data. The source package does not include the original protocol, adverse event data, disposition data, eligibility data, concomitant medication data, efficacy assessments, randomization metadata, or study drug accountability details. Those records should be incorporated from source systems or original study documents before using this as anything beyond an example protocol.

